 Total Team Spending and Profitability Results in a Higher League Ranking in the English Premier League

### 2024-04-19 paper/paper.qmd
Test.

```{r}
#| label: tbl-8
#| tbl-cap: Actual vs Predicted Points for English Premier League Teams Based on Home Attendance, Wage Bill, and Market Value, Sorted by Current League Ranking in Descending Order
#| echo: false
#| warning: false

@@

>>>>

```{r}
#| label: tbl-8
#| tbl-cap: Actual vs Predicted Points for English Premier League Teams Based on Home Attendance, Total Payroll, and Market Value, Sorted by Current League Ranking in Descending Order
#| echo: false
#| warning: false

@@

```{r}
#| label: tbl-9
#| tbl-cap: Actual Rank vs Predicted Rank Based on Home Attendance, Total Payroll, and Market Value for English Premier League Teams
#| echo: false
#| warning: false

# Add predicted points to 'analysis_data'
analysis_data$predicted_pts <- predict(model, newdata = analysis_data)

# Prepare the predicted rankings
predicted_table <- analysis_data |>
  arrange(desc(predicted_pts)) |>  # Sort by predicted points in descending order
  mutate(predicted_rank = row_number()) |>  # Assign ranking based on predicted points
  select(team, predicted_rank) |>
  rename(`Predicted Standings` = team, `Predicted Rank` = predicted_rank)

# Prepare the actual rankings
actual_table <- analysis_data |>
  arrange(desc(pts)) |>  # Sort by actual points in descending order
  mutate(actual_rank = row_number()) |>  # Assign ranking based on actual points
  select(team, actual_rank) |>
  rename(`Actual Standings` = team, `Rank` = actual_rank)

# Merge both tables based on rank
result_table <- merge(actual_table, predicted_table, by.x = "Rank", by.y = "Predicted Rank")

# Select only the desired columns: Rank, Actual Standings, and Predicted Standings
final_result <- result_table |>
  select(Rank, `Actual Standings`, `Predicted Standings`)

# Format table with LaTeX and apply additional styling
kable(final_result, booktabs = TRUE, align = c("r", "l", "l"), "latex", longtable = TRUE) |>
  kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10)
```
